State change and diversity animations

### 2022-11-15 index.Rmd
update index
mostly animation code updated

[The Supplementary Report (HTML page)](./experiments/2_supplement/supplement.html)

[HTML page about how to reproduce the research.](./docs/How_to_reproduce.html)

[Some animations of results (HTML page)](./experiments/3_animate/report.html)

>>>>

[The respository on Zenodo with DOI 10.5281/zenodo.6334544.](https://doi.org/10.5281/zenodo.6334544)

[The Supplementary Report (HTML page)](./reports/supplement/supplement_0.9.1.html)

[Instructions of how to reproduce the research (HTML page).](./docs/How_to_reproduce.html)

[Some animations of results (HTML page)](./reports/animations/report.html)

### 2022-11-15 reports/animations/report.Rmd
mostly animation code updated

```{r}
include_graphics(here("experiments/3_animate/mp4s/CB_no_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/CB_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/SB_no_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/SB_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/PB_no_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/PB_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/O_no_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/O_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/SR_no_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/SR_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/SO_no_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/SO_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/P_no_div.mp4"))
```

@@

```{r}
include_graphics(here("experiments/3_animate/mp4s/P_medium_div.mp4"))
```

>>>>

```{r}
include_graphics(here("reports/animations/mp4s/CB_no_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/CB_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/SB_no_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/SB_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/PB_no_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/PB_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/O_no_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/O_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/SR_no_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/SR_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/SO_no_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/SO_medium_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/P_no_div.mp4"))
```

@@

```{r}
include_graphics(here("reports/animations/mp4s/P_medium_div.mp4"))
```
